Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-10-20 text/ms.tex
Remove unnecessary word

Here we develop a probabilist framework for identifying ecological black swans
in population dynamic process noise --- the stochastic jumps from time step to
time step. Our framework quantifies both the magnitude and probability of
heavy-tailed dynamics, allows for a range of population dynamic models, can
incorporate observation uncertainty, and is applicable to commonly available
lengths of abundance time series. We apply our model to hundreds of populations
from around the world across four taxonomic classes to address three questions:
(1) how frequent and strong are black swans in population dynamics across
taxonomy, (2) what are some verified causes of black swans in ecological time
series, and (3) are there characteristics of time series or intrinsic
life-history characteristics associated with heavy-tailed dynamics. We find
a high probability of ecological black swans across a wide range of taxa but in
a limited number of populations. When they occur, extreme climate, predation,
parasites, and their interactions are common documented causes. We find little
evidence that intrinsic life-history characteristics are related to the
probability of black swans.

>>>>

Here we develop a framework for identifying ecological black swans in
population dynamic process noise --- the stochastic jumps from time step to
time step. Our framework quantifies both the magnitude and probability of
heavy-tailed dynamics, allows for a range of population dynamic models, can
incorporate observation uncertainty, and is applicable to commonly available
lengths of abundance time series. We apply our model to hundreds of populations
from around the world across four taxonomic classes to address three questions:
(1) how frequent and strong are black swans in population dynamics across
taxonomy, (2) what are some verified causes of black swans in ecological time
series, and (3) are there characteristics of time series or intrinsic
life-history characteristics associated with heavy-tailed dynamics. We find
a high probability of ecological black swans across a wide range of taxa but in
a limited number of populations. When they occur, extreme climate, predation,
parasites, and their interactions are common documented causes. We find little
evidence that intrinsic life-history characteristics are related to the
probability of black swans.
